%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Lead Platform Engineer} % Job title
    {Constructor.io} % Organization
    {San Francisco, CA, United States} % Location
    {Nov. 2023 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Everything that matters.}
        \item {Designed and provisioned the entire infrastructure on the AWS cloud to meet security compliance and acquire a business license for financial services in Korea.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {DevOps Engineer} % Job title
    {} % Organization
    {} % Location
    {Jun. 2023 - Oct. 2023} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {
        \textbf{Instagram Server Release} (Jan 2022 - Present)
        \begin{itemize}
          \item {designing and building release processes and infrastructure, to continuously rollout Instagram product code}
          \item {collaborating and aligning with many different teams in Instagram - webserver, developer experience, products, ...}
          \item {managing projects, timelines and expectations with stakeholders}
        \end{itemize}
      }
      \item {
        \textbf{Elasticsearch} (Jan 2020 - Jan 2022)
        \begin{itemize}
          % TODO: filter some stuff out
          \item {designing, building and maintaining all of Elasticsearch infrastructure at Meta}
          \item {working with teams using Elasticsearch to understand their needs and onboard them}
          \item {designed cluster architecture and integration with Meta systems; entire cluster lifecycle management}
          \item {implemented a continuous integration and deployment solution for Elasticsearch clusters - CI/CD pipelines with custom monitoring and push strategies}
        \end{itemize}
      }
      \item {
        \textbf{Vulnerability Management} (Nov 2018 - Jan 2020)
        \begin{itemize}
          \item {building distributed systems architecture to discover and manage vulnerabilities in all of Meta infrastructure}
          \item {helping build "Vulnerability Management-as-a-Service" - self serviced vulnerability discovery, monitoring and alerting}
          \item {working with external partners (companies) on integrating multiple vulnerability providers into our system to broaden coverage and increase discovery speed}
          \item {cross functional work with numerous other teams to help them surface vulnerabilities in their libraries/repositories/services/hosts and helping them remediate}
          \item {one of the core maintainers of Meta's opensource tools and libraries for managing vulnerability data (\href{https://github.com/facebookincubator/nvdtools}{nvdtools})}
        \end{itemize}
      }
      \item {
        \textbf{Misc}
        \begin{itemize}
          \item {interviewing candidates for jobs at Meta - coding and systems (Linux) interviews for engineers}
          \item {primary point of contact ("bootcamp mentor") for Meta newcomers - assigning tasks, tracking progress, helping with team selection, introducing the Meta culture}
          \item {helping new team members with onboarding - finding tasks and projects, explaining how the systems work, etc.}
          \item {presenting on internal conferences at Meta}
          \item {\href{https://www.youtube.com/watch?v=wP3OpdfOYok}{presented my life journey} as an engineer to numerous Middle schools across the UK, as part of the Primary Engineer Programme}
        \end{itemize}
      }
    \end{cvitems}
  }

%---------------------------------------------------------
  \cventry
    {Site Reliability Engineer} % Job title
    {Superbet} % Organization
    {Zagreb, Croatia} % Location
    {Mar. 2022 - Jun. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Distributed tracing setup, both infrastructure and application layers.}
        \item {Kafka connect deployment.}
        \item {Load testing Kubernetes clusters on AWS with k6.io.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Lead Software Engineer} % Job title
    {} % Organization
    {} % Location
    {Jan. 2021 - Feb. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Leading development and maintenance of 13 production services on a betting platform that has 350 000 unique visitors a month, 30 000 bets per hour and 30 000 Kafka messages per second}
        \item {Replaced legacy bet acceptance solution. Improved scalability from 80req/s to 6400req/s}
        \item {Conducting 1on1 meetings with 4 team members, supporting their technical growth}
        \item {Interviewing new candidates, engineering roles}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {} % Organization
    {} % Location
    {Jun. 2019 - Dec. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Development of an event-driven sports betting system}
        \item {Bet acceptance, Payment, Offer and Risk integration}
        \item {Responsible for online solution delivery}
        \item {Introduced: In-house Redis library, Kubernetes health checks, gRPC load balancing}
        \item {Design documents, Code reviews, Unit and E2E testing}
        \item {System monitoring and service metric collection with Prometheus and Grafana}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Researcher} % Job title
    {Undergraduate Research, Machine Learning Lab(Prof. Seungjin Choi)} % Organization
    {Pohang, S.Korea} % Location
    {Mar. 2016 - Exp. Jun. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Researched classification algorithms(SVM, CNN) to improve accuracy of human exercise recognition with wearable device.}
        \item {Developed two TIZEN applications to collect sample data set and to recognize user exercise on SAMSUNG Gear S.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer \& Security Researcher (Compulsory Military Service)} % Job title
    {R.O.K Cyber Command, MND} % Organization
    {Seoul, S.Korea} % Location
    {Aug. 2014 - Apr. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Lead engineer on agent-less backtracking system that can discover client device's fingerprint(including public and private IP) independently of the Proxy, VPN and NAT.}
        \item {Implemented a distributed web stress test tool with high anonymity.}
        \item {Implemented a military cooperation system which is web based real time messenger in Scala on Lift.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Game Developer Intern at Global Internship Program} % Job title
    {NEXON} % Organization
    {Seoul, S.Korea \& LA, U.S.A} % Location
    {Jan. 2013 - Feb. 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed in Cocos2d-x an action puzzle game(Dragon Buster) targeting U.S. market.}
        \item {Implemented API server which is communicating with game client and In-App Store, along with two other team members who wrote the game logic and designed game graphics.}
        \item {Won the 2nd prize in final evaluation.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Researcher for <Detecting video’s torrents using image similarity algorithms>} % Job title
    {Undergraduate Research, Computer Vision Lab(Prof. Bohyung Han)} % Organization
    {Pohang, S.Korea} % Location
    {Sep. 2012 - Feb. 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Researched means of retrieving a corresponding video based on image contents using image similarity algorithm.}
        \item {Implemented prototype that users can obtain torrent magnet links of corresponding video relevant to an image on web site.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer Trainee} % Job title
    {Software Maestro (funded by Korea Ministry of Knowledge and Economy)} % Organization
    {Seoul, S.Korea} % Location
    {Jul. 2012 - Jun. 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Performed research memory management strategies of OS and implemented in Python an interactive simulator for Linux kernel memory management.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {ShitOne Corp.} % Organization
    {Seoul, S.Korea} % Location
    {Dec. 2011 - Feb. 2012} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed a proxy drive smartphone application which connects proxy driver and customer. Implemented overall Android application logic and wrote API server for community service, along with lead engineer who designed bidding protocol on raw socket and implemented API server for bidding.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Freelance Penetration Tester} % Job title
    {SAMSUNG Electronics} % Organization
    {S.Korea} % Location
    {Sep. 2013, Mar. 2011 - Oct. 2011} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Conducted penetration testing on SAMSUNG KNOX, which is solution for enterprise mobile security.}
        \item {Conducted penetration testing on SAMSUNG Smart TV.}
      \end{cvitems}
      %\begin{cvsubentries}
      %  \cvsubentry{}{KNOX(Solution for Enterprise Mobile Security) Penetration Testing}{Sep. 2013}{}
      %  \cvsubentry{}{Smart TV Penetration Testing}{Mar. 2011 - Oct. 2011}{}
      %\end{cvsubentries}
    }

%---------------------------------------------------------
\end{cventries}
